Amortization of Sub-programs in Simulators

### 2019-08-28 paper/learning/notes.tex
updated

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{graphicx}
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{listings}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{pgfplots}
\usepackage{tikz,pgf}
\usepackage{todonotes}
\usepackage{tikz-cd}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{wrapfig}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{cancel}
\usepackage{wrapfig}

\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
\tikzset{>=latex}
\usetikzlibrary{bayesnet}
\usetikzlibrary{arrows,shapes,automata}
\usetikzlibrary{positioning}

\newcommand{\n}[1]{\ensuremath{n_{#1}}}
\newcommand{\rv}[1]{\ensuremath{{#1}_{1:n_{#1}}}}
\newcommand{\rvv}[1]{\ensuremath{{#1}_{1:n_{#1'}}}}
\newcommand{\model}[1]{\ensuremath{\mathcal{M}{(#1)}}}
\newcommand{\simu}[1]{\ensuremath{\Omega(\model{#1})}}
\newcommand{\micro}[2]{\ensuremath{\phi_{#1}(#2)}}
\newcommand{\pdf}[1]{\ensuremath{\mathcal{P}_{d}(#1)}}
\newcommand{\pmf}[1]{\ensuremath{\mathcal{P}_{m}(#1)}}
\newcommand{\add}[1]{\ensuremath{A_{#1}}}
\newcommand{\adds}[2]{\ensuremath{A_{#1}_{#2}}}
\newcommand{\expect}[1]{\ensuremath{\mathbb{E}[#1]}}
\newcommand{\trace}[1]{\ensuremath{\mathcal{T}_{#1}}}
\newcommand{\traces}[2]{\ensuremath{\textit{tr}^{#1}_{#2}}}
\newcommand{\stoc}[2]{\ensuremath{f^{#1}_{#2}(\rvv{x})}}
% \usepackage[binary-units=true]{siunitx}
\title{Amortization of Sub-programs in Simulators }%\\ for Fast Simulator Inference}

@@

\lstset{language=C++,
                basicstyle=\footnotesize,
                keywordstyle=\color{blue}\ttfamily,
                stringstyle=\color{red}\ttfamily,
                commentstyle=\color{green}\ttfamily,
                morecomment=[l][\color{magenta}]{\#},
                breaklines = true
}
\pgfplotsset{width=7cm,compat=1.8}
\author{%
Paper ID: 1010 }
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
%}
\begin{document}
% \nipsfinalcopy is no longer used

@@

\section{Nested-Programs within Simulators}

@@

To construct the mathematical framework in this setting we employ the notation of~\cite{rainforth2017automating}, 
where \emph{raw samples} are represented by $ f_{a_i}(x_i | \eta)$ and can be thought of as prior terms.

@@

\section{Amortized Rejection Sampling}

@@

\bibliography{refs}
\bibliographystyle{iclr2020_conference}
\appendix

\section{The unconditional acceptance probability}

>>>>

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{graphicx}
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{listings}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{pgfplots}
\usepackage{tikz,pgf}
\usepackage{todonotes}
\usepackage{tikz-cd}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{wrapfig}
\usepackage{amsmath,amsthm}
\usepackage{amssymb}
\usepackage{cancel}
\usepackage{wrapfig}
\usepackage{amssymb}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
\tikzset{>=latex}
\usetikzlibrary{bayesnet}
\usetikzlibrary{arrows,shapes,automata}
\usetikzlibrary{positioning}
\lstnewenvironment{cpp}
{\lstset{language=C++,
  basicstyle=\footnotesize,
  keywordstyle=\color{blue}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  commentstyle=\color{green}\ttfamily,
  morecomment=[l][\color{magenta}]{\#},
  breaklines = true,
  stringstyle=\color{blue}\ttfamily, % typewriter type for strings, blue 
  showstringspaces=false,
  postbreak=\raisebox{0ex}[0ex][0ex]{\color{red}$\hookrightarrow$\space},
}}{}
\newcommand{\n}[1]{\ensuremath{n_{#1}}}
\newcommand{\rv}[1]{\ensuremath{{#1}_{1:n_{#1}}}}
\newcommand{\rvv}[1]{\ensuremath{{#1}_{1:n_{#1'}}}}
\newcommand{\model}[1]{\ensuremath{\mathcal{M}{(#1)}}}
\newcommand{\simu}[1]{\ensuremath{\Omega(\model{#1})}}
\newcommand{\micro}[2]{\ensuremath{\phi_{#1}(#2)}}
\newcommand{\pdf}[1]{\ensuremath{\mathcal{P}_{d}(#1)}}
\newcommand{\pmf}[1]{\ensuremath{\mathcal{P}_{m}(#1)}}
\newcommand{\add}[1]{\ensuremath{A_{#1}}}
\newcommand{\adds}[2]{\ensuremath{A_{#1}_{#2}}}
\newcommand{\expect}[1]{\ensuremath{\mathbb{E}[#1]}}
\newcommand{\trace}[1]{\ensuremath{\mathcal{T}_{#1}}}
\newcommand{\traces}[2]{\ensuremath{\textit{tr}^{#1}_{#2}}}
\newcommand{\stoc}[2]{\ensuremath{f^{#1}_{#2}(\rvv{x})}}
% \usepackage[binary-units=true]{siunitx}
\title{Amortization of Sub-programs in Simulators }%\\ for Fast Simulator Inference}

@@

% \lstset{language=C++,
%                 basicstyle=\footnotesize,
%                 keywordstyle=\color{blue}\ttfamily,
%                 stringstyle=\color{red}\ttfamily,
%                 commentstyle=\color{green}\ttfamily,
%                 morecomment=[l][\color{magenta}]{\#},
%                 breaklines = true
% }
\pgfplotsset{width=7cm,compat=1.8}
\author{%
Paper ID: 1010 }
  % examples of more authors
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \AND
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
  % \And
  % Coauthor \\
  % Affiliation \\
  % Address \\
  % \texttt{email} \\
%}
\begin{document}
% \nipsfinalcopy is no longer used

@@

\section{Sub-Programs within Simulators}

@@

Sub-programs, all called nested programs~\cite{}
To construct the mathematical framework in this setting we employ the notation of~\cite{rainforth2017automating}, 
where \emph{raw samples} are represented by $ f_{a_i}(x_i | \eta)$ and can be thought of as prior terms.

@@

\section{Amortized Sub-programs}

@@

\bibliography{refs}
\bibliographystyle{iclr2020_conference}

%%%%%%% Appendix %%%%%%%%
\appendix

\section{Code Examples of Stochastic Processes in Simulators }

The following examples are taken from SHERPA~\cite{gleisberg2009event}
a million-line plus code base used for the modelling of complex physics
simulators at CERN.

\small\begin{table}[]
  \begin{tabular}{|l|l|l|l|}
  \hline
  \textbf{Code} & \textbf{Base} & \textbf{Timed} & \textbf{Stochastic Control Flow} \\ \hline
  \begin{cpp}
  double Splitter_Base::SelectZ(const double & delta,
  const bool & lead)
   {double zmin(0.5*(1.-sqrt(1.-delta))),
   zmax(0.5*(1.+sqrt(1.-delta))), z;
    do {
      z = zmin+ran->Get()*sqrt(1.-delta);
        } 
    while (1.-2.*z*(1.-z) < ran->Get());
  return z;
   }
  \end{cpp}&Yes&No&Yes\\ 
  \hline
  \begin{cpp}
double Decay_Channel::GenerateMass(const double& max,
const double& width) const
{
 double mass=-1.0;
 double decaymin = MinimalMass();
 if(decaymin>max) mass=-1.0;
 else if (decaymin==0.0) {
   mass=m_flavours[0].RelBWMass(decaymin, max,
                p_ms->Mass(m_flavours[0]), width);
      }
 else {
   double s=sqr(p_ms->Mass(GetDecaying()));
   double mb(0.0), mc(0.0);
   for (int i=0; i<NOut(); ++i) {
     mc+=p_ms->Mass(GetDecayProduct(i));
     if(p_ms->Mass(GetDecayProduct(i))>mb)
       mb=p_ms->Mass(GetDecayProduct(i));
   }
   mc-=mb;
   double b=sqr(mb);
   double c=sqr(mc);
   double spmax=2.0*b+2.0*c+sqrt(sqr(b)+14.0*b*c+sqr(c));
   double wmax=MassWeight(s,spmax,b,c);
   double w=0.0;
   int trials(0);
   do {
     mass=m_flavours[0].RelBWMass(decaymin, max,
                                  p_ms->Mass(m_flavours[0]), width);
     double sp=sqr(mass);
     w=MassWeight(s,sp,b,c);
     ++trials;
   } while (w<ran->Get()*wmax && trials<1000);
 }
 return mass;
}
\end{cpp}
        &  No             & Yes                     & No  \\ \hline
                &               &                     &                                  \\ \hline
  \end{tabular}
  \end{table}
\section{The unconditional acceptance probability}
